---
title: "Wordle_Challenge"
author: "SLCornett"
date: "2/10/2022"
output: html_document
---
Preliminary
```{r}
library(tidyverse)
library(readr)
library(dplyr)
library(sjmisc)
```
**Step 1**

New Function: Load Dictionary
```{r}
load_dictionary<-function(filename){
  w=read.delim(filename)
  w$words
} 
```
New Variable/Vector: Valid List
```{r}
valid_list<-load_dictionary("collins-scrabble-words-2019")
str(valid_list)
```
New Variable: Solution List
```{r}
solution_list <- load_dictionary("google-10000-english-usa-no-swears.txt")
str(solution_list)
```
**Step 2**
Solution list including only words in valid list
```{r}
#Intersect(value, value), not intersection('')
solution_list<-intersect(solution_list, valid_list)
str(solution_list) 
```
Now, only 8336 words in the list. 

**Step 3**

New Function: Pick Solution
[1] removes all words from solution_list that are not 5 letters in length, 
[2] then randomly chooses a single word from those that remain, and 
[3] then splits that word into a vector of single-character elements
```{r}
pick_solution<-function(solution_list,word_length=5){
  sl <- as.data.frame(solution_list)
  names(sl) <- c("word")
  sl <- dplyr::filter(sl, nchar(word)==word_length)
  word<-dplyr::sample_n(sl, size=1)
  word<-word$word %>%
    strsplit(word, split = "")
  print(word)
}
solution <-pick_solution(solution_list, word_length = 5)
```

**Step 4**
should take three arguments: [1] the answer to the puzzle (the value of your solution variable), [2] a list of valid guesses (the contents of your valid_list variable), and [3] a value for “number of guesses,” which you should set to the original Wordle game default of 6.
```{r}
#helper function
evaluate_guess<-function(guess, solution){
  library(sjmisc)
  word_length<-length(solution)
  text_result<-rep("-", word_length)
  for (i in 1:word_length){
    text_result[i]<- case_when(
      guess[i] %in% solution & guess[i]==solution[i] ~  "*",
      guess[i] %in% solution & guess[i]!=solution[i] ~  "+",
      guess[i] %nin% solution[i] ~  "-"
    )
    print(text_result)
  }
}
```

```{r}
#playwordle
play_wordle <- function(solution, valid_list, num_guesses=6){
  library(tidyverse)
  library(sjmisc)
  word_length<-length(solution)
  print(paste0("Welcome to a R-Wordle. You have", num_guesses, " chances to guess a word with", word_length, "letters. Try not to get killed along the way. Best of luck!"))
  print("Available Letters:")
  letters_left<-LETTERS
  print(letters_left)
  guess_history<-data.frame(matrix(nrow=num_guesses, ncol=word_length))
  results_history<-data.frame(matrix(nrow=num_guesses, ncol=word_length))
  for(i in 1:num_guesses){
    guess <- readline("Please input your word guess, then press Enter/Return to submit your guess:") %>%
    toupper()
    guess <- strsplit(guess, split = "") [[1]]
    print(guess)
    result<-evaluate_guess(guess, solution)
    letters_left<-setdiff(letters_left, guess)
    print(letters_left)
    }
  return(result) 
  return(letters_left)
}

play_wordle(solution, valid_list, num_guesses=6)  
```
